An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-11 paper.tex
Note that Chester's data isn't available.

Chester et. al~\cite{Chester2007} report on a large gait database comparison
where one database contained kinematic data of 409 gait cycles of children
from 1 to 7 years old. Tirosh et. al, recognized the need of a comprehensive
data base for clinical gait data and created the Gaitabase~\cite{Tirosh2010}.
This database may contain a substantial amount of data but it is encumbered by
a very complicated and restrictive license and sharing scheme. The University
of Wisconsin at LaCrosse has a normative gait data set~\cite{Wilson} from 25
subjects with lower extremity marker data and force plate measurements from a
single stance phase.

>>>>

Chester et. al~\cite{Chester2007} report on a large gait database comparison
where one database contained kinematic data of 409 gait cycles of children from
1 to 7 years old but the data does not seem to be publicly available. Tirosh
et. al, recognized the need of a comprehensive data base for clinical gait data
and created the Gaitabase~\cite{Tirosh2010}.  This database may contain a
substantial amount of data but it is encumbered by a very complicated and
restrictive license and sharing scheme. The University of Wisconsin at LaCrosse
has a normative gait data set~\cite{Wilson} from 25 subjects with lower
extremity marker data and force plate measurements from a single stance phase.
